HUME: Human UCCA-Based Evaluation of Machine Translation

### 2016-09-15 paper/main.tex
hmeant comparison

%This is not entirely true - they do allow an alignment with partial
%Conversely, HMEANT does not penalize errors (e.g., incorrect tense or negation flip) in a correctly aligned predicate:
%
%\begin{center}
%\begin{tabular}{lp{5.4cm}}
%Source & \small ... don't skip meals ... \\
%Transl.& \small ... nicht {\"u}berspringen Mahlzeiten ... \\
%Gloss & \small ... don't skip meals ... \\
%\end{tabular}
%\end{center}
%While the translation is mostly understandable, the verb {\"u}berspringen is incorrectly inflected. HUME allows marking the %main verb as Orange, while
%marking the translation of the argument (``Malhzeiten'' or ``meals'') as correct. HMEANT may only mark the predicate as %correct, or mark the entire argument structure as an error.

@@

>>>>

@@

In other cases, HMEANT's does not to penalize errors. For instance, as HMEANT is defined as an aggregate
of the scores given to the slot fillers, it cannot assign partial scores to the predicates themselves in
cases of a divergent tense or a negation flip. Consider the following:

\begin{center}
\begin{tabular}{lp{5.4cm}}
Source & \small ... don't skip meals ... \\
Transl.& \small ... nicht {\"u}berspringen Mahlzeiten ... \\
Gloss & \small ... don't skip meals ... \\
\end{tabular}
\end{center}

The translation is mostly understandable, although the verb ``{\"u}berspringen'' is incorrectly inflected.
HUME allows marking it as Orange (as it was  indeed annotated in our experiments), while
HMEANT allows either to mark it as correct, or otherwise mark the entire frame as a ``no match''.
